Tourism Data Analysis

### 2020-01-17 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.Rmd
Calculating ME

---
title: "Tourism Data Analysis"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
date: "31 July 2019"
---

@@

# Log Transformation with 100 observations of training window (Average MSE calculated over 140 replications)

@@

DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100

DF_LogTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1

@@

# Log Transformation with 180 observations of training window (Average MSE calculated over 60 replications)

@@

DF_LogTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL180

DF_LogTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_MSE_h1

@@

# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (Average MSE calculated over 140 replications)

@@

DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100

DF_BoxCoxTrans_WL100 %>%
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
  filter(Forecast_Horizon == 1) %>%
  ungroup() %>%
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_MSE_h1

Avg_BoxCox_WL100_MSE_h1 %>%
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
  spread(key = F.method, value = MSE) %>%
  kable(format = "latex")

@@

# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (Average MSE calculated over 60 replications)

@@

DF_BoxCoxTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL180

DF_BoxCoxTrans_WL180 %>%
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
  filter(Forecast_Horizon == 1) %>%
  ungroup() %>%
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL180_MSE_h1

Avg_BoxCox_WL180_MSE_h1 %>%
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
  spread(key = F.method, value = MSE) %>%
  kable(format = "latex")

>>>>

---
title: "Tourism Data Analysis"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
date: "Jan 2020"
---

@@

# Log Transformation with 100 observations of training window (ME and MSE calculated over 140 replications)

@@

DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100
DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL100

# ME
DF_LogTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_LogTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1

@@

# Log Transformation with 180 observations of training window (ME and MSE calculated over 60 replications)

@@

DF_LogTrans_WL180 <- DF_LogTrans_WL180 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_LogTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL180
DF_LogTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL180

# ME
DF_LogTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_ME_h1

Avg_Log_WL180_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_LogTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_MSE_h1

@@

# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (ME and MSE calculated over 140 replications)

@@

DF_BoxCoxTrans_WL100 <- DF_BoxCoxTrans_WL100 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100
DF_BoxCoxTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL100

# ME
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_BoxCoxTrans_WL100 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1

@@

# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (ME and MSE calculated over 60 replications)

@@

DF_BoxCoxTrans_WL180 <- DF_BoxCoxTrans_WL180 %>% 
  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
# so that we don't confuse Biased forecasts with ME

DF_BoxCoxTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL180
DF_BoxCoxTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL180

# ME
DF_BoxCoxTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1

Avg_Log_WL100_ME_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = ME) %>% 
  kable(format = "latex",)

#MSE
DF_BoxCoxTrans_WL180 %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1
